\texttt{davos}: a Python package ``smuggler'' for constructing lightweight reproducible notebooks

### 2022-11-15 paper/main.tex
WIP illustrative example section, saving to branch off and implement davos dir

>>>>

Next, the user smuggles a pair of packages that extend the Jupyter notebook interface with various interactive JavaScript widgets. The \texttt{ipywidgets}~\cite{GrouEtal15} package provides an API for creating these widgets with Python code, and the \texttt{widgetsnbextension} package provides the machinery for the notebook frontend to display them. Thus, \texttt{ipywidgets} must be installed in the same environment as the IPython kernel, and \texttt{widgetsnbextension} must be installed in the environment that houses the Jupyter notebook server. In the simplest case, these two environments are the same; however, a common approach to using Jupyter notebooks with multiple different Python environments (e.g., for different tasks or projects) is to run the notebook server from a ``base environment,'' with additional environments each providing their own separate, interchangeable IPython kernels. (While possible to detect programmatically, Figure~\ref{fig:illustrative-example} assumes this setup to simplify the example code.) To handle this multi-environment installation, line 25 temporarily changes the \texttt{pip} executable used to install smuggled packages to that of the notebook server's environment before smuggling \texttt{widgetsnbextension} (line 26). Since there is no need to actually load this package for later use in the analysis code, it is aliased as a single underscore---by convention, a ``throwaway'' variable in Python. In line 27, the user changes the \texttt{pip} executable back to that of the notebook kernel environment (its original value) before installing \texttt{ipywidgets} and subsequent packages. With these two packages installed, line 30 smuggles \texttt{tqdm}~\cite{CaspEtal22}, which provides convenient progress bars for long-running code. In Jupyter notebooks, the \texttt{tqdm.notebook} module can be imported to enable prettier progress bars displayed via \texttt{ipywidgets}, if that package is installed and importable. Therefore, in this case, it was important to \texttt{smuggle}

% In Jupyter notebooks, \texttt{tqdm} will attempt to display these progress bars using \texttt{ipywidgets} if the package is installed and available.

%managing multiple, interchangeable IPython kernels is to run the notebook server from a ``base environment,'' with additional Python environments each providing its own separate kernel (e.g.,

Finally, the user loads in the ... but in order to successfully ... they must deal with a similar problem to ...
